The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (9th edition -- distributed with CrypTool version 1.4.20)} \vspace{60pt}

### 2009-07-01 script/en/script-en.tex
Add an appendix on using Sage with this script
Change copyright years to the range 1998--2009

\documentclass[a4paper,11pt,oneside]{book}
\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}

\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
%\bibliographyunit[\section] % bibunits für das ganze Dokument aktivieren
\defaultbibliography{references}
\defaultbibliographystyle{abbrv}

@@

\author{
Copyright (c) Prof.\ Bernhard Esslinger (co-author and editor) \\
and the CrypTool Development Team, 1998-2008 \\
Frankfurt am Main, Germany\\*[1ex]
\url{www.cryptool.org}
}

@@

\newpage
\normalsize
\parindent 0cm
\parskip 4pt

@@

\begin{appendix}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/authors.tex}
  \input{chapters/gnu-fdl-1.3.tex}
\end{appendix}

>>>>

\documentclass[a4paper,11pt,oneside]{book}
\setlength{\fboxrule}{.5mm}
\setlength{\fboxsep}{1.75mm}
\setlength{\footnotesep}{6pt}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}

\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage{url}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
%\bibliographyunit[\section] % bibunits für das ganze Dokument aktivieren
\defaultbibliography{references}
\defaultbibliographystyle{abbrv}

@@

\author{
Copyright (c) Prof.\ Bernhard Esslinger (co-author and editor) \\
and the CrypTool Development Team, 1998-2009 \\
Frankfurt am Main, Germany\\*[1ex]
\url{www.cryptool.org}
}

@@

\newpage
\normalsize
%\parindent 0cm
\parskip 4pt

@@

\begin{appendix}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/authors.tex}
  \input{chapters/gnu-fdl-1.3.tex}
  \input{chapters/what-is-sage.tex}
\end{appendix}
